---
title: "MTCars Dashboard"
output: 
  flexdashboard::flex_dashboard:
    theme:
      version: 3
      bootswatch: flatly
      base_font:
        google: Prompt
      code_font:
        google: JetBrains Mono
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(crosstalk)
library(DT)
library(plotly)
# library(d3scatter)
library(summarywidget)

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

mtCarsSD <- mtcars |> 
  rownames_to_column(var = "model") |> 
  mutate(cyl = factor(cyl),
         vs = if_else(vs == 0, "V-Shaped", "Inline"),
         am = if_else(am == 0, "Automatic", "Manual")) |> 
  SharedData$new()

```

Column {data-width=650 .tabset}
-----------------------------------------------------------------------

### Fuel Mileage by Horsepower

```{r}

mtCarsSD |> 
  plot_ly(x=~hp, y=~mpg, color=~cyl, 
          type="scatter", mode="markers", 
          marker = list(size=12,
                        line=list(width=2, color="black")),
          colors = "Set2",
          text=~paste0(model, "<br>", disp, " cu. in.<br>", gear, " gears")) |> 
  layout(xaxis=list(title="Horsepower"),
         yaxis=list(title="Miles per Gallon"),
         legend=list(title=list(text="Cyl.")))

```

### Fuel Mileage by Displacement

```{r}

mtCarsSD |> 
  plot_ly(x=~disp, y=~mpg, color=~cyl, 
          type="scatter", mode="markers", 
          marker = list(size=12,
                        line=list(width=2, color="black")),
          colors = "Set2",
          text=~paste0(model, "<br>", hp, " HP<br>", gear, " gears")) |> 
  layout(xaxis=list(title="Displacement (cu. in.)"),
         yaxis=list(title="Miles per Gallon"),
         legend=list(title=list(text="Cyl.")))

```

### Boxplots
```{r}

plotCyl <- mtCarsSD |> 
  plot_ly(x=~cyl, y=~mpg,  
          type="box", boxpoints="all", pointpos=0,
          marker = list(size=12, line=list(width=2, color="black")),
          colors = "Set2",
          text=~paste0(model)) |> 
  layout(xaxis=list(title="Cylinders"))


plotTrans <- mtCarsSD |> 
  plot_ly(x=~am, y=~mpg,  
          type="box", boxpoints="all", pointpos=0,
          marker = list(size=12, line=list(width=2, color="black")),
          colors = "Set2",
          text=~paste0(model)) |> 
  layout(xaxis=list(title="Transmission"))

subplot(plotCyl, plotTrans, titleX=T) |> 
  layout(yaxis=list(title="Miles per Gallon")) |> 
  hide_legend()

```

### Data Table

```{r}

datatable(mtCarsSD)

```

Column {data-width=350}
-----------------------------------------------------------------------

### Filters

```{r}

filter_checkbox("cyl", "Cylinders", mtCarsSD, ~cyl, inline=T)
filter_checkbox("am", "Automatic", mtCarsSD, ~am, inline = T)
filter_checkbox("gear", "Num. of Gears", mtCarsSD, ~gear, inline = T)
filter_checkbox("vs", "Engine Shape", mtCarsSD, ~vs, inline = T)
filter_slider("disp", "Displacement", mtCarsSD, ~disp)
```

### Summary

Of the **`r summarywidget(mtCarsSD, "count")`** cars:

  - **`r summarywidget(mtCarsSD, "count", selection=~am=="Automatic")`** are Automatic
  - **`r summarywidget(mtCarsSD, "count", selection=~am=="Manual")`** are Manual

The average fuel mileage is:

 - All selected cars: **`r summarywidget(mtCarsSD, "mean", "mpg")`** MPG
 - Automatic cars: **`r summarywidget(mtCarsSD, "mean", selection=~am=="Automatic", "mpg")`** MPG 
 - Manual cars: **`r summarywidget(mtCarsSD, "mean", selection=~am=="Manual", "mpg")`** MPG